Final Model Analysis

### 2017-09-25 model fitting/final_model.Rmd
minor edits

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
x <- oshitar::variable_setup(out)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
x <- oshitar::variable_setup(out)
x <- x[[1]]
